\documentclass[10pt]{article} % Font size, can be: 10pt, 11pt or 12pt
\usepackage[utf8]{inputenc}

\usepackage{enumitem}
\setlist{leftmargin=4.5mm}

\usepackage{sectsty}
\subsectionfont{\fontsize{10}{10}\selectfont}

\usepackage{xcolor}
\definecolor{light-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}

\input{structure.tex}

\begin{document}

\begin{paracol}{2}

\parbox[top][0.12\textheight][c]{\linewidth}{
	\vspace{-0.04\textheight}
	\centering
	{\sffamily\Huge Philippe Fanaro}\\\medskip
	{\huge\color{headings} Data Scientist}
}

\section{Main Qualifications}

\begin{itemize}
    \itemsep0em
    \item \textbf{Electrical Engineering Graduate (BSc)} from the \textbf{University of São Paulo}, with an international exchange experience in Brussels (\textbf{Uni-versité Libre de Bruxelles}) through a government scholarship program (Science without Borders).
    \item \textbf{Programming Languages}: \code{\small Python}, \code{\small SQL}, \code{\small JavaScript}, \code{\small R}, \code{\small MatLab}, \code{\small HTML}.
    \item \textbf{Machine Learning}, \textbf{Neural Networks}, \textbf{Deep Learning}.
    \item Experience with \textbf{Process Improvements} in a Start Up of the tech sector.
    \item Advanced knowledge of \textbf{Excel} and \textbf{LaTeX}.
    \item International Experience: \textbf{Belgium (1 year)} e \textbf{South Korea (6 months)}.
\end{itemize}

\section{Education} 

\begin{supertabular}{rl}
\educationentry{2011 -- 2016}
{University of São Paulo (USP)}
{Electrical Engineering}
{}
{}
\educationentry{2015 -- 2016} % Duration
{Université Libre de Bruxelles (ULB)}
{Science without Borders (SwB)}
{}
{}
\end{supertabular}

\section{Experience}

\workposition{Aug 2016 -- Dec 2016}
{}
{Vital Care App}
{Intern}
{\textrightarrow \ Improvements of the Customer Service, Marketing and SEO plans. \\ \textrightarrow \  App User Interface (UI) enhancements. \\ \textrightarrow \ Investigated problems with some clients’ sanitary infractions.}

\section{Personal Information}

    \subsection*{Go | Baduk | Weiqi}
    
        \begin{itemize}
        
            \itemsep0em
            \item Brazilian representative at the 12\textsuperscript{th} Korean Prime Minister Cup (KPMC).
            \item 6-month stay in South Korea in the 2nd semester of 2017 to improve my skills in the game.
            \item 1\textsuperscript{st} place (4\textsuperscript{th} in the open division) among the Brazilians in the 2018 Brazil Cup.
            
        \end{itemize}

    \subsection*{My Website}
    
        \begin{itemize}
        
            \itemsep0em
            \item Creator of a website featuring many diverse topics (fanaro.com.br), such as Data Science, Politics, Literature, Go, among others.
            
        \end{itemize}

%------------------------------------------------

\switchcolumn

\parbox[top][0.12\textheight][c]{\linewidth}{
	\vspace{-0.04\textheight}
	\colorbox{shade}{
		\begin{supertabular}{p{0.05\linewidth}|p{0.775\linewidth}}
		
        	\raisebox{-1pt}{\faPhone} & +55 (11) 97028-6739 \\
        	
        	\raisebox{-1pt}{\faMale} & 26 years old \\
        	
			\raisebox{-1pt}{\faHome} & Chácara Sto. Antônio - São Paulo - SP, Brazil \\
			
			\raisebox{0pt}{\small\faEnvelope} & \href{mailto:philippefanaro@gmail.com}{philippefanaro@gmail.com} \\
			
            \raisebox{-1pt}{\small\faLinkedinSquare} & \href{https://www.linkedin.com/in/philippe-fanaro/}{linkedin.com/in/philippe-fanaro} \\
            
			\raisebox{-1pt}{\small\faLaptop} & \href{http://fanaro.com.br/}{fanaro.com.br} \\
			
			\raisebox{-1pt}{\small\faGithub} & \href{https://github.com/psygo}{github.com/psygo} \\
			
		\end{supertabular}
	}
}

\section{Idiomas} 

\begin{supertabular}{rl}

	%------------------------------------------------
	
	\educationentry{2017}
	{English}
	{Fluent}
	{TOEFL ibT 103/120}
	{}
	
	%------------------------------------------------
	
	\educationentry{2016}
	{French}
	{Fluent}
	{Français Langue Étrangère, ULB}
	{}
	
	%------------------------------------------------
	
	\educationentry{2017}
	{Korean}
	{Basic}
	{6 Months in South Korea}
	{}
	
	%------------------------------------------------
	
	\educationentry{2016}
	{Chinese}
	{Basic}
	{3 Months of Private Lessons}
	{}
	
	%------------------------------------------------

\end{supertabular}

\section{Extracurricular Courses}

%------------------------------------------------

\begin{supertabular}{rl}
	
	%------------------------------------------------
	
	\tableentry{2018}{\textbf{Deeplearning.ai}}{spaceafter}
	\tableentry{}{Neural Networks and Deep Learning}{}
	\tableentry{}{Improving Neural Networks}{}
	\tableentry{}{Structuring Machine Learning Projects}{}
	\tableentry{}{Convolutional Neural Networks}{}
	\tableentry{}{Sequence Models}{spaceafter}
	
	%------------------------------------------------
	
	\tableentry{2018}{\textbf{Udemy}}{spaceafter}
	\tableentry{}{The Ultimate MySQL Bootcamp}{}
	\tableentry{}{Financial Analysis \& Algorithmic Trading}{}
	\tableentry{}{Probability and Statistics for Data Science}{}
	\tableentry{}{Deep Learning A-Z: Neural Networks}{}
	\tableentry{}{The Complete JavaScript Course 2018}{spaceafter}
	%------------------------------------------------
	
	\tableentry{2015 -- 2016}{\textbf{Université Libre de Bruxelles}}{spaceafter}
	\tableentry{}{Cryptography}{}
	\tableentry{}{RF Design}{}
	\tableentry{}{Nonlinear Modelling}{}
	\tableentry{}{High Frequency Electronics}{spaceafter}
	
	%------------------------------------------------
	
	\tableentry{2015}{\textbf{USP (Post-Graduation)}}{spaceafter}
	\tableentry{}{Matrix Analysis for Electrical Engineering}{spaceafter}
	
	%------------------------------------------------
	
	\tableentry{2014}{\textbf{Nuclear Research Institute (IPEN-USP)}}{spaceafter}
	\tableentry{}{Monte Carlo for Radiation Applications}
	
	%------------------------------------------------

\end{supertabular}

\section{Other Information}

\begin{itemize}

    \itemsep0em
    \item Swimming and Water Polo competitive athlete for the Esporte Clube Pinheiros (ECP) for 10 years.
    \item Diverse leisure reading about technical (the Law, recently, for example), human sciences (microsociology) and literature.
    \item Also an advanced player of other strategy games, such as Poker and Backgammon.
    
\end{itemize}

\end{paracol}

%----------------------------------------------------------------------------------------

\end{document}
