\documentclass[14pt]{extarticle}

% ----------------------------------------------------------
% Config

\usepackage[colorlinks, allcolors = black]{hyperref}
\usepackage[margin = 2.5cm]{geometry}

\renewcommand{\labelitemii}{$\circ$}

\renewcommand{\_}{\leavevmode\kern.06em\vbox{\hrule width.425em}}

% Paragraph Formatting

\setlength{\parindent}{0pt}
\linespread{1.2}

% Quote Formatting

\usepackage{mdframed}
\usepackage{xcolor}

\mdfdefinestyle{CSSquote}{
  linecolor         = black!50!black,
  linewidth         = 2.5pt,
  topline           = false,
  rightline         = false,
  bottomline        = false,  
  backgroundcolor   = white!10,
  innerleftmargin   = 10pt,
  innerrightmargin  = 15pt,
  innertopmargin    = 6.5pt,
  innerbottommargin = 6pt,
  skipabove         = 15pt,
  skipbelow         = 15pt
}

\newenvironment{cssquote}{%
  \begin{mdframed}[style=CSSquote]
}{%
  \end{mdframed}
}

% ----------------------------------------------------------
% Title

\title{\scshape \huge \vspace{-1.5cm} Philippe Fanaro}
\author{%
  \scshape \Large Full Stack Developer\\[0.5cm]%
  \scshape \Large React | Next.js%
  \vspace{0.6cm}%
}
\date{}

% ----------------------------------------------------------

\begin{document}

\maketitle

\section{Summary}

Four years of professional experience, with a primary stack of \textbf{Next.js}, \textbf{React}, \textbf{TypeScript}. As well as extensive experience in \textbf{Python}, \textbf{Flutter}, \textbf{SQL}, \textbf{NoSQL}, and \textbf{Firebase}. Other technologies I'm also proficient in would be: \textbf{React Native}, \textbf{AWS}, \textbf{Lit} (Web Components), \textbf{Three.js}, and \textbf{Java}.

\vspace{0.4cm}

\begin{cssquote}
Check out my portfolio and blog: \textbf{\href{https://neofanaroio.vercel.app}{neofanaroio.vercel.app}}.
\end{cssquote}

\section{Work Experience}

\begin{enumerate}
  \item \textbf{Go (Board Game) Teacher} \textit{(Feb 2025 -- Jun 2026)}
    \begin{itemize}
      \item Online and In Person
      \item Went to Korea and Japan to perfect my skills in the game of Go (Baduk or Weiqi), while also teaching online and in person. 
      \begin{itemize}
        \item The summary video of my one year experience in Asia: \\ \href{https://youtu.be/apgV3qMGfmg}{youtu.be/apgV3qMGfmg} 
      \end{itemize}
    \end{itemize}

  \item \textbf{Full Stack Developer} @ Vertical Insure \textit{(Feb 2023 -- Jun 2023)}
    \begin{itemize}
      \item In charge of the frontend and Web Component development.
      \item Helped with the backend and the devops.
      \item Tech Stack:
        \begin{itemize}
          \item Frontend: React, Lit Framework, JS | TS
          \item Backend: Java, Micronaut, NodeJS, Express
          \item DevOps: AWS, Render, DataDog, Retool, etc.
        \end{itemize}
    \end{itemize}

  \item \textbf{Go (Board Game) Teacher} \textit{(Jun 2021 -- Aug 2022)}
    \begin{itemize}
      \item Managed an online school and league.
      \item Created video lectures and reviews.
      \item Streamed events.
    \end{itemize}
    
  \item \textbf{Open Source Developer} @ Fast Immutable Collections (FIC) \textit{(Oct 2020 -- Jan 2021)}
    \begin{itemize}
      \item Co-developed a popular data structure package for Dart (Flutter):\\
      \href{https://github.com/marcglasberg/fast\_immutable\_collections}{github.com/marcglasberg/fast\_immutable\_collections}.
      \item Applied Test-Driven Development (TDD) to the whole project.
    \end{itemize}
    
  \item \textbf{Data Scientist} @ Zanthus \textit{(Feb 2019 -- Oct 2019)}
    \begin{itemize}
      \item Worked on creating a new CRM system based on data science and machine learning.
      \item Tech Stack: Python, Pandas, NumPy, Scikit-learn, and SQL.
      \item Responsibilities:
      \begin{itemize}
        \item Data extraction
        \item Preprocessing
        \item Modeling
      \end{itemize}
    \end{itemize}
\end{enumerate}

\section{Education}

\begin{enumerate}
  \item \textbf{Electrical Engineering (BSc)} @ Universidade de São Paulo (USP) \textit{(2011 -- 2016)}
    \begin{itemize}
      \item The best university in South America.
      \item Specializing in telecommunications.
      \item (Engineering degrees take 5 years in Brazil.)
    \end{itemize}

  \item \textbf{International Engineering Exchange} @ Université Libre de Bruxelles (ULB) \textit{(2015 -- 2016)}
    \begin{itemize}
      \item One year abroad in Brussels, Belgium, studying engineering, \linebreak through a government scholarship.
      \item Perfected my English
      \item Learned French.
    \end{itemize}
\end{enumerate}

\section{Projects}

\begin{itemize}
  \item \textbf{\href{https://neofanaroio.vercel.app}{neofanaroio.vercel.app}
} \textit{(Jun 2026 -- Today)}
    \begin{itemize}
      \item My personal portfolio and blog, built with Next.js and TailwindCSS.
      \item The new version of my old, basic blog, \href{https://github.com/psygo/fanaro.io}{fanaro.io}.
    \end{itemize}
    
  \item \textbf{Magi} \textit{(Sep 2025 -- Dec 2025)} 
    \begin{itemize}
      \item A 2D exploration of the internet, using SQL and Excalidraw to create a graph database.
      \item \href{https://github.com/psygo/magi}{github.com/psygo/magi}
    \end{itemize}
    
  \item \textbf{Aquarifolio} \textit{(Sep 2025 -- Dec 2025)}
    \begin{itemize}
      \item A 3D aquarium containing most of my work, done with Three.js and React.
      \item \href{https://github.com/psygo/aquarifolio}{github.com/psygo/aquarifolio}
    \end{itemize}
    
  \pagebreak

  \item \textbf{Go (Board Game) Techniques Book} \textit{(Sep 2024 -- Nov 2024)}
    \begin{itemize}
      \item A book on Go (board game), entirely made with \LaTeX , and a custom package for drawing vector diagrams with TikZ/PGF.
      \item \href{https://github.com/psygo/tecnicas\_de\_go}{github.com/psygo/tecnicas\_de\_go}
    \end{itemize}
    
  \item \textbf{YouTube KBD Nav} \textit{(Sep 2021 -- Oct 2021)}
    \begin{itemize}
      \item A browser extension for navigating YouTube solely through the keyboard.
      \item \href{https://github.com/psygo/youtube\_kbd\_nav}{github.com/psygo/youtube\_kbd\_nav}
    \end{itemize}
  
  \item \textbf{Go Book Translation} \textit{(Aug 2021 -- Sep 2021)}
    \begin{itemize}
      \item Official translation and editing (\LaTeX) of an introductory book on Go, from English to Portuguese.
      \item \href{https://github.com/psygo/traducao\_como\_jogar\_go}{github.com/psygo/traducao\_como\_jogar\_go}
    \end{itemize}
    
  \item \textbf{fanaro.io} \textit{(Aug 2021 -- Sep 2021)}
    \begin{itemize}
      \item My old blog, with no frameworks, HTML, CSS, and Web Components.
      \item \href{https://github.com/psygo/fanaro.io}{github.com/psygo/fanaro.io}
    \end{itemize}
\end{itemize}

\section{Technologies}

\begin{itemize}
  \item Main Stack: 
    \begin{itemize}
      \item React
      \item Next.js
      \item TypeScript
      \item SQL
      \item Tailwind CSS
      \item HTML
      \item CSS
    \end{itemize}
    
  \item Other technologies I have worked with:
    \begin{itemize}
      \item Flutter/Dart
      \item Web Components
      \item Lit (Web Components)
      \item Three.js
      \item React Native
      \item Firebase
      \item \LaTeX
    \end{itemize}
  \item Data Science/Analytics stack I have worked with:
    \begin{itemize}
      \item Python
      \item SQL
      \item Pandas
      \item NumPy
      \item Scikit-learn
    \end{itemize}
  \item Other technologies I use or have used:
    \begin{itemize}
      \item Java
      \item Shell
      \item Vim
      \item TikZ/PGF
    \end{itemize}
\end{itemize}

\section{Languages}

\vspace{0.2cm}

\hbox{
  \hspace{0.05cm}
  \renewcommand{\arraystretch}{1.25}
  \setlength{\tabcolsep}{0.5cm}

  \begin{tabular}{ l | l  }
    \textbf{Language} & \textbf{Proficiency} \\
    \hline\hline
    Portuguese & Native \\
    English & Fluent \\
    French & Advanced \\
    Spanish & Intermediate \\
    Korean & Basic \\
    Japanese & Basic
  \end{tabular}
}

\vspace{1.1cm}

\section{Personal Interests}

On my free time, I enjoy reading and watching videos about psychology, history, philosophy and economics.

\vspace{0.4cm}

I'm also a big fan of board games in general, not only of Go (Baduk or Weiqi). Among other board games I'm a fan of: backgammon, shogi, Blokus.

\vspace{0.4cm}

And I regularly post articles and videos on my blog (\href{https://neofanaroio.vercel.app}{neofanaroio.vercel.app}) and YouTube channels, on Go, software, psychology, and a variety of different topics.

\section{Personal Information}

\vspace{0.7cm}

\hbox{
  \hspace{0.05cm}
  \renewcommand{\arraystretch}{1.25}
  \setlength{\tabcolsep}{0.5cm}

  \begin{tabular}{ l | l }
    \textbf{Birthday} & June 27th, 1992 \\
    \textbf{Location} & São Paulo, Brazil \\
    \textbf{Phone} & +55 (11) 97028-6739 \\
    \textbf{Email} & \href{mailto:philippefanaro@gmail.com}{philippefanaro@gmail.com} \\
    \textbf{Blog} & \href{https://neofanaroio.vercel.app/}{neofanaroio.io} \\
    \textbf{LinkedIn} & \href{https://www.linkedin.com/in/philippe-fanaro/}{linkedin.com/in/philippe-fanaro} \\
    \textbf{GitHub} & \href{https://github.com/psygo}{github.com/psygo}
  \end{tabular}
}

\end{document}